---
title: "STAT 605 Project"
author: "Group 5"
output:
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE,warning = FALSE,cache = TRUE)
```

[Link to Github Repository](https://github.com/anchayes/Stat605_Project)

### Project Proposal  

Using the 31G flight data set from Kaggle, we will analyze ticket prices based on 
departing airport. The data is from Expedia between 2022-04-16 and 2022-10-05. 
The airport arrival/destinations are ATL, DFW, DEN, ORD, LAX, CLT, MIA, JFK, 
EWR, SFO, DTW, BOS, PHL, LGA, IAD, OAK. 

### Description of Variables :  
legId: An identifier for the flight.  
searchDate: The date (YYYY-MM-DD) on which this entry was taken from Expedia.  
flightDate: The date (YYYY-MM-DD) of the flight.  
startingAirport: Three-character IATA airport code for the initial location.  
destinationAirport: Three-character IATA airport code for the arrival location.  
fareBasisCode: The fare basis code.  
travelDuration: The travel duration in hours and minutes.  
elapsedDays: The number of elapsed days (usually 0).  
isBasicEconomy: Boolean for whether the ticket is for basic economy.  
isRefundable: Boolean for whether the ticket is refundable.  
isNonStop: Boolean for whether the flight is non-stop.  
baseFare: The price of the ticket (in USD).  
totalFare: The price of the ticket (in USD) including taxes and other fees.  
seatsRemaining: Integer for the number of seats remaining.  
totalTravelDistance: The total travel distance in miles.   

### Code to Read Data:  
[Link to data](https://www.kaggle.com/datasets/dilwong/flightprices)

```{r,fig.width=1}
require(gt)
require(data.table)
flights=fread("itineraries.csv",nrows=1000)

head(flights,n=5) %>%
  gt()
```


### Statistical Methods
We will use multiple linear regression to predict the price of a flight. 

### Computational Steps
1. Split data into several smaller files by departing airport

2. Use best subset or some other variable selection method to chose which variables are significant to price

3. Fit a model and run diagnostics 

Steps 2 and 3 will be distributed to the departing airport files.

